---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "README-"
)
```

# readMDTable
<!-- badges: start -->
[![R-CMD-check](https://github.com/jrdnbradford/readMDTable/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jrdnbradford/readMDTable/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

readMDTable converts raw markdown tables from a string, file, or URL to tibbles. 

Many sites (like GitHub) convert markdown tables into HTML tables. For these types of tables you're probably better off using [rvest](https://rvest.tidyverse.org/).

## Installation

Install from GitHub:
```{r, eval=FALSE}
devtools::install_github("jrdnbradford/readMDTable")
```

## License
GPL >= 3.

## Docs

Review the [package index reference](https://jrdnbradford.github.io/readMDTable/reference/index.html) or use
```{r, eval=FALSE}
?readMDTable
```
for documentation.

## Example

```{r, echo=FALSE, include=FALSE}
devtools::load_all()
```

Read in an example markdown table from the package:
```{r}
mtcars_file <- read_md_table_example("mtcars.md")
```

The raw markdown table:
```{r}
cat(readLines(mtcars_file), sep = "\n")
```

After reading it in:
```{r}
read_md_table(mtcars_file)
```
