---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# readMDTable
<!-- badges: start -->
[![R-CMD-check](https://github.com/jrdnbradford/readMDTable/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jrdnbradford/readMDTable/actions/workflows/R-CMD-check.yaml)
[![Dev status](https://img.shields.io/github/r-package/v/jrdnbradford/readMDTable/main?label=Dev%20Version&style=flat-square&logo=github)](https://github.com/jrdnbradford/readMDTable)
<!-- badges: end -->

readMDTable converts raw markdown tables from a string, file, or URL to tibbles. 

Many sites (like GitHub) convert markdown tables into HTML tables. For these types of tables you're probably better off using [rvest](https://rvest.tidyverse.org/).

## Installation

Install from GitHub:
```{r, eval=FALSE}
devtools::install_github("jrdnbradford/readMDTable")
```

## Docs

Review the [package index reference](https://jrdnbradford.github.io/readMDTable/reference/index.html) or use
```{r, eval=FALSE}
?readMDTable
```
for documentation.

## Usage

### From a File
```{r, echo=FALSE, include=FALSE}
devtools::load_all()
```

Read in an example markdown table from the package:
```{r}
mtcars_file <- read_md_table_example("mtcars.md")
```

The raw markdown table:
```{r}
cat(readLines(mtcars_file, 10), sep = "\n")
```

After reading it in:
```{r}
read_md_table(mtcars_file)
```

### From a String
```{r}
read_md_table("| len | supp | dose |\n|---|---|---|\n| 4.2 | VC | 0.5 |")
```

### From a URL
```{r}
read_md_table("https://raw.githubusercontent.com/jrdnbradford/readMDTable/main/inst/extdata/iris.md")
```

### Warnings and Messy Data
readMDTable will throw warnings if there are potential issues with the markdown table. In many cases it will still correctly read in the messy data:
```{r}
read_md_table(
"  | Name   | Age |            City        | Date   |
|-------|-----|-------------|------------|
  | Alice |      30 |           | 2021/01/08 |
  | Bob          | 25  | Los Angeles | 2023/07/22      
  | Carol | 27       | Chicago     |      |"
)
```

## License
GPL >= 3.
